---
title: "HR_Zip14_MEMRITimecourse_Analyses"
author: "Hari Rallapalli"
date: "10/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
```
```{r}
strcorrect <- function(x){
  x %>% noquote() %>% gsub(", ",",",.) %>% gsub("\\[|\\]", "", .) %>% gsub("[\r\n]", "", .) %>% str_split(.," ")
}
```

```{r}
df <- read.csv("\\\\nindsdirfs2\\shares\\LFMI\\FMM\\Shared\\rallapallih\\Zip14\\RawImages\\Analysis\\VoxelWiseIntensities.csv", header = TRUE, stringsAsFactors = FALSE) %>%
  mutate(values = sapply(values,strcorrect))
```

```{r}
df <- df %>% 
  mutate(timepoint = ifelse(str_detect(image,"00hrs"),0,
                            ifelse(str_detect(image,"04hrs"),4,
                            ifelse(str_detect(image,"08hrs"),8,
                            ifelse(str_detect(image,"12hrs"),12,
                            ifelse(str_detect(image,"24hrs"),24,
                            ifelse(str_detect(image,"48hrs"),48,
                            ifelse(str_detect(image,"01week"),168,
                            -1))))))))
```

```{r}
df <- df %>% 
  mutate(condition = ifelse(str_detect(image,"Cryocoil"),"No Injection",
                            ifelse(str_detect(image,"Zip14"),"Zip14",
                                   "YFP")))
```

```{r}
df <- df %>% 
  mutate(mouse = sub("_T.*", "", image)) %>%
  mutate(sex = ifelse(str_detect(mouse,"_F"),"Female","Male"))
```

```{r}
df <-  df %>% mutate(values = as.numeric(unlist(values)))
```

               
               
               col.names = c("V1" = "Filenames", "V2" = "PCL", "V3" = "WM", "V4" = "ML", "V5" = "IGL")) %>%
  mutate(mouse = str_extract(Filenames, "PCP2CRE_B\\d+_\\w\\d*"),
         maptype = "T1") %>% 
  group_by(mouse) %>%
  mutate(toxin = ifelse(str_detect(mouse,"_C"),"NoDTR","DTR"),
         batch = str_extract(mouse,"B\\d"),
         background = sub("_.*", "", mouse)) %>%
  mutate(PCL = sapply(PCL,strcorrect),
         WM = sapply(WM,strcorrect),
         ML = sapply(ML,strcorrect),
         IGL = sapply(IGL,strcorrect)) %>%
  gather(roi,measurement,PCL,WM,ML,IGL) %>% 
  unnest() %>%
  mutate(measurement = (1000/as.numeric(measurement))) %>%
  arrange(mouse) %>%
  na.omit()
```
